General purpose gene annotation using deep learning

### 2020-01-10 paper/main.tex
rewrite metric part paper

We use metrics two metrics to judge model performance. The {\it Genic F1} is our primary metric that provides the most comprehensive picture of annotation quality in one number. The {\it Subgenic F1} is similar to the Genic F1, except that it does not take UTR prediction quality into account. This is done for comparability with Augustus and further explained in chapter \ref{augustus}. Both metrics work by summing up True Positives (TP), False Positives (FP), etc of each considered class before calculating precision, recall and ultimatily a F1 score. Both metrics do also leave out the intergenic class, as this is by far the easiest to predict and could potentially skew the results too far away from the performance in the genic region. The Genic F1 thus essentially provides a weighted mean of the classes UTR, CDS and Intron while the Subgenic F1 sums up only CDS and Intron. All individual class performances are reported in the Suplementary Material (?).

>>>>

We use metrics two metrics to judge model performance. The {\it Genic F1} is our primary metric that provides the most comprehensive picture of annotation quality in one number. The {\it Subgenic F1} is similar to the Genic F1, except that it does not take UTR predictions into account. This is done for comparability with Augustus and further explained in Chapter \ref{augustus}. Both metrics work by summing up True Positives (TP), False Positives (FP) and False Negatives (FN) of each considered class before calculating precision and recall from these values and combining the two into a F1 score. Both metrics do not take the values of the intergenic class into account, as this class is very abundant and appears to be by far the easiest to predict. In the case of the Genic F1, this means that effectively only the TP of the intergenic class are disregarded. The metrics essentially provide a weighted mean of the performances in the considered classes. All individual class performances are reported in Suplementary Material (?).
